A loop quantum gravity inspired action for the bosonic string and emergent dimensions at large scales

### 2025-10-23 AoP/final-proof/aop-format.tex
Final version of published article

Now, one might object and say that having an action which is the sum of two Nambu--Goto actions seems strange. However, similar actions have been extensively studied under the heading of ``bimetric gravity'', with the
earliest work dating as far back as 1940 in two papers~\cite{Rosen1940General,Rosen1940aGeneral} by Einstein's future collaborator Nathan Rosen (the `R' in `EPR' and `ER'). In 2010, bimetric gravity gained great popularity
due to the seminal paper~\cite{de-Rham2011Resummation} which showed that by introducing a second {reference} metric into a model for massive gravity one can get rid of the Boulware--Deser
ghost~\cite{Boulware1972Can-Gravitation} which otherwise plagues theories with massive gravitons. The {reference} metric introduced in the work~\cite{de-Rham2011Resummation} was taken to be a flat metric. However
later work~\cite{Hassan2012Bimetric,Hassan2012Ghost-Free} showed that the second metric need not be flat and that an action of the following form:
\begin{eqnarray}
\xlabel{eqn:hassan-bimetric}
\nf&& S = M_g^2 \int \diff^4 x \sqrt{-g} R^{(g)} + M_f^2 \int \diff^4 x \sqrt{-f} R^{(f)} + \nonumber\\\nf&&\xq
+ 2 m^2 M^2_{eff} \int \diff^4 x \sqrt{-g}\sum_{n=0}^{4}\beta_n e_n (\sqrt{g^{-1} f}),
\end{eqnarray}
where $g_{\mu\nu}$ and $f_{\mu\nu}$ are {arbitrary} metrics, $M_g^2, M_f^2$ are the Planck masses for the two sectors respectively. $R^{(g)}, R^{(f)}$ are the respective Ricci scalars for each sector. The third term is an interaction term which is responsible for making one of the gravitons massive while the other remains massless. $M^2_{eff}$ is an {effective} Planck mass given by:
\begin{equation}
\xlabel{eqn:hassan-effective-mpl}
M^2_{eff} = \left( \frac{1}{M^2_g} + \frac{1}{M^2_f} \right)^{-1}
\end{equation}

@@

Following the general procedure given in~\cite{Callan1985Strings}, we can couple the worldsheet to a bulk metric as follows:
\begin{equation}
\xlabel{eqn:polyakov-curved}
S_{P} = -\frac{T}{2} \int \diff^2 x \sqrt{-g} g^{ab} \partial_a X^\mu \partial_b X^\nu G_{\mu\nu},
\end{equation}
where $G_{\mu\nu}$ is now the bulk or target space metric. Using this form we can now write down the worldsheet Polyakov bimetric action for two bulk metrics:
\begin{eqnarray}
\xlabel{eqn:polyakov-bimetric}
\nf&& S_{PB} = -\frac{T}{2} \int \diff^2 x\sqrt{-g} g^{ab} \partial_a X^\mu \partial_b X^\nu G_{\mu\nu} - \nonumber\\\nf&&\xq
- \frac{T'}{2} \int \diff^2 x \sqrt{-h} h^{ab} \partial_a X^\mu \partial_b X^\nu H_{\mu\nu} +  \nonumber\\\nf&&\xq
+ S_{int} [g, h, X].
\end{eqnarray}

@@

\nf&& T^{(G)} _{c d} \coloneq  G_{\mu \nu} \biggm( \partial _{c} X^{\mu} \partial _{d} X^{\nu} - \nonumber\\\nf&&\xq

@@

\nf&& T^{(H)} _{c d} \coloneq  H_{\mu \nu} \biggm( \partial _{c} X^{\mu} \partial _{d} X^{\mu} - \nonumber\\\nf&&\xq

@@

\nf&&\left( \delta _{a} ^{c'} \delta _{b} ^{d'} H_{\mu \nu} - \frac{1}{2 g} \Delta _{a c} \varepsilon ^{c c'} \Delta _{b d} \varepsilon ^{d d'} G_{\mu \nu} \right) \times\nonumber \\\nf&&\xq

@@

S_{I A P}& =& - \frac{T}{2} \int \diff ^2 x \left( \sqrt{- g} - \frac{k \Delta}{2 \sqrt{- g}} \right) \times\nonumber \\\nf&& \times g^{a b} \partial _{a} X^{\mu} \partial _{b} X^{\nu} G_{\mu \nu} .

@@

The equations of motion for the world-sheet metric are completely unchanged by this correction,
\begin{equation}
 \xlabel{eqn:vary-wrt-g}
\frac{\delta S_{I A P}}{\delta g^{c d}} = 0
\end{equation}
which leads to the stress--energy tensor for the worldsheet:
\begin{eqnarray}
 \xlabel{eqn:inverse-area-em-tensor}
\nf&& T_{c d} \coloneq  \partial _{c} X^{\mu} \partial _{d} X^{\nu} G_{\mu \nu} - \nonumber\\ \nf&&\xq - \frac{1}{2} g_{c d} g^{a b} \partial _{a} X^{\mu} \partial _{b} X^{\nu} G_{\mu \nu} = 0,
\end{eqnarray}
from which we can extract the metric $g_{c d}$ as
\begin{equation}
 \xlabel{eqn:ws-metric}
g_{c d} = 2 f \partial _{c} X^{\mu} \partial _{d} X^{\nu} G_{\mu \nu},
\end{equation}
where the function $f$ is given by
\begin{equation}
 \xlabel{eqn:inverse-area-f}
\frac{1}{f} = g^{a b} \partial _{a} X^{\mu} \partial _{b} X^{\nu} G_{\mu \nu}
\end{equation}
just like the regular ST literature, thus the constraints are unchanged by our correction.

As for variation \wrt \ the embbeding fields $X^{\lambda}$, we have
\begin{equation}
 \xlabel{eqn:vary-wrt-X}
\frac{\delta S_{I A P}}{\delta X^{\lambda}} = 0
\end{equation}
\begin{eqnarray}
 \xlabel{eqn:X-eom-inverse-area}
\nf&& F^{-} \sqrt{- g} g^{a b} \partial _{a} \partial _{b} X^{\nu} G_{\lambda \nu} + \partial _{a} \left( F^{-} \sqrt{- g} g^{a b} \right) \partial _{b} X^{\nu} G_{\lambda \nu} =\nonumber \\\nf&&\xq = \frac{1}{2} F^{-} \sqrt{- g} g^{a b} \partial _{a} X^{\mu} \partial _{b} X^{\nu} \partial _{\lambda} G_{\mu \nu},
\end{eqnarray}
where
\begin{equation}
 \xlabel{eqn:F-minus-def}
F^{-} \equiv 1 - \frac{k \Delta}{2 (- g)} .
\end{equation}
Since all 2-dimensional metrics are conformally flat~\cite{Schottenloher2008A-Mathematical}, we use conformal gauge $g_{a b} = \e ^{\phi (x)} \eta _{a b}$ and assume flat background $G_{\mu \nu} = \eta _{\mu \nu}$, to simplify Eq. \neqref{eqn:X-eom-inverse-area} into
\begin{equation}
 \xlabel{eqn:X-eom-simplified}
\eta ^{a b} \partial _{a} \partial _{b} X^{\mu} + \frac{1}{F^{-}} \eta ^{a b} \partial _{a} F^{-} \partial _{b} X^{\mu} = 0 .
\end{equation}
By expanding the definition of $F^{-}$ we get
\begin{equation}
 \xlabel{eqn:coupling-X-phi}
\eta ^{a b} \partial _{a} \partial _{b} X^{\mu} + \eta ^{a b} \frac{\left( 2 \del _{a} \phi - \del _{a} \ln (\Delta) \right)}{\dfrac{2 \e ^{2 \phi}}{k \Delta} - 1} \del _{b} X^{\mu} = 0,
\end{equation}
revealing a wave equation sourced by a coupling between the WS conformal factor, quantum of area field $\Delta$ and the embedding fields much akin to the dilaton field~\cite{Balthazar-t-backgrounds}. We will come back to
this in \xref{sec:emergent-dimensions}.

@@

If one were to calculate the equations of motion for the quantum of area field $\Delta _{a b}$ in the actions \neqref{eqn:modified-ng-action,eqn:inverse-metric-Polyakov} explored before, one would end up concluding that
either $\Delta _{a b} = 0$ or its determinant $\Delta = 0$ vanish. This happens because, as we explored in  \xref{sec:ws-kalb-ramond}, $\Delta _{a b}$ is actually related to the pullback of the Kalb--Ramond field $B_{\mu \nu}$, but
those actions were actions for the free string, not coupled to said field. The more complete picture would be thus to consider the (area-corrected) string now coupled to the Kalb--Ramond field~\cite{Tong2009Lectures}
\begin{eqnarray}
 \xlabel{eqn:area-corrected-K-R-action}
S &=& - \frac{1}{4 \pi \alpha '} \int \diff ^2 x \left( \sqrt{- g} - \frac{1}{2} \frac{k \Delta}{\sqrt{- g}} \right) \times \nonumber\\\nf&&\xq
\times \Bigl( g^{a b} \del _{a} X^{\mu} \del _{b} X^{\nu} G_{\mu \nu} - \varepsilon ^{a b} \del _{a} X^{\mu} \del _{b} X^{\nu} B_{\mu \nu} \Bigr),
\end{eqnarray}
where  we can rewrite $\varepsilon ^{a b}$ in terms of $\Delta ^{a b}$ as
\begin{eqnarray}
 \xlabel{eqn:area-corrected-K-R-action-v2}
S &=& - \frac{1}{4 \pi \alpha '} \int \diff ^2 x \left( \sqrt{- g} - \frac{1}{2} \frac{k \Delta}{\sqrt{- g}} \right) \times\nonumber \\
&&\times \Bigm( g^{a b} \del _{a} X^{\mu} \del _{b} X^{\nu} G_{\mu \nu} - \nonumber\\\nf&&
- \sqrt{\Delta} \Delta ^{a b} \del _{a} X^{\mu} \del _{b} X^{\nu} B_{\mu \nu} \Bigm) .
\end{eqnarray}
By varying this action \wrt $\Delta ^{c d}$ we get
\begin{equation}
 \xlabel{eqn:Delta-pullback}
\Delta _{c d} = \widetilde{f} \del _{c} X^{\mu} \del _{d} X^{\nu} B_{\mu \nu}
\end{equation}
with $\widetilde{f}$ given by
\begin{eqnarray}
 \xlabel{eqn:1/f-tilde}
\frac{1}{\widetilde{f}} &=& \frac{1}{g + \dfrac{k \Delta}{2}} \Biggm( \frac{k \sqrt{\Delta}}{2} g^{a b} \del _{a} X^{\mu} \del _{b} X^{\nu} G_{\mu \nu} - 
\nonumber\\\nf&&- \left( g + \frac{3 k \Delta}{4} \right) \Delta ^{a b} \del _{a} X^{\mu} \del _{b} X^{\nu} B_{\mu \nu} \Biggm),
\end{eqnarray}
where if we take $g_{a b} = \del _{a} X^{\mu} \del _{b} X^{\nu} G_{\mu \nu}$ and $\del _{a} X^{\mu} \del _{b} X^{\nu} B_{\mu \nu} = \Delta _{a b} / \widetilde{f}$ this simplifies to
\begin{equation}
 \xlabel{eqn:f-tilde}
\widetilde{f} = - \frac{g + k \Delta}{k \sqrt{\Delta}},
\end{equation}
from which it is easy to see that the pullback of the Kalb--Ramond field $b_{a b} \coloneq  \del _{a} X^{\mu} \del _{b} X^{\nu} B_{\mu \nu}$ is given by
\begin{equation}
 \xlabel{eqn:WS-b-field}
b_{a b} = - \frac{1}{\dfrac{g}{k \Delta} + 1} \varepsilon _{a b},
\end{equation}
or equivalently that the relation between $\Delta _{a b}$ and $b_{a b}$ is
\begin{equation}
 \xlabel{eqn:Delta-b-relation}
\Delta _{a b} = \sqrt{\Delta} \varepsilon _{a b} = - \sqrt{\Delta} \left( \frac{g}{k \Delta} + 1 \right) b_{a b} .
\end{equation}
We thus see that the pullback of the Kalb--Ramond field is actually a tensor {density} of weight $- 1$, since the coefficient in Eq. \neqref{eqn:WS-b-field} is a true scalar and the Levi-Civita symbol is itself a density.

@@

\eqref{eqn:X-eom-simplified} seems a bit odd, but we can polish it by choosing a plane-wave ansatz for the embedding fields $X^{\mu} = X^{\mu} _{0} \e ^{-i (E \tau - p \sigma)}$ and using it to fix a form for the conformal factor $\e ^{\phi (x)}$ appearing in $F^{-}$. By using the ansatz in Eq. \neqref{eqn:X-eom-simplified}, it becomes
\begin{equation}
(E^{2} - p^{2}) X^{\mu} + i (E \partial _{\tau} \ln (F^{-}) - p \partial _{\sigma} \ln (F^{-})) X^{\mu} = 0,
\end{equation}
from which we can use the freedom in the conformal factor to fix the second term as $- \mu ^2 X^{\mu}$, with $- \mu ^2 = p^2 - E^2$ on-shell and this, in turn, implies that the derivatives of $\ln (F^{-})$ are given by
\begin{equation}
 \xlabel{eqn:derivatives-F-minus}
\partial _{\tau} \ln (F^{-}) = i E, \ \partial _{\sigma} \ln (F^{-}) = i p,
\end{equation}
thus we have
\begin{equation}
 \xlabel{eqn:ln-F}
\ln (F^{-}) = i (E \tau + p \sigma) + a, \ a \in \mathbb{C}
\end{equation}
\xpar\cvskip[-9pt]
\begin{equation}
 \xlabel{eqn:F-minus-exp}
F^{-} = A \e ^{i (E \tau + p \sigma)}, \ A \in \C
\end{equation}
\xpar\cvskip[-9pt]
\begin{equation}
 \xlabel{eqn:phi}
\e ^{\phi (x)} = \sqrt{\frac{k \Delta}{2 \left( 1 - A \e ^{i (E \tau + p \sigma)} \right)}} .
\end{equation}
It may seem problematic to have a complex conformal factor, but the complex structure comes from our ansatz for the embedding fields, and when we choose either the real or imaginary part of the latter it should also pick the respective component of $\e ^{\phi}$. With this choice, we thus turned Eq. \neqref{eqn:X-eom-simplified} into a Klein--Gordon equation
\begin{equation}
 \xlabel{eqn:X-Klein-Gordon-eqn}
\left( \partial _{\sigma} ^2 - \partial _{\tau} ^2 \right) X^{\mu} - \mu ^2 X^{\mu} = 0 .
\end{equation}
The imposition that
\begin{equation}
 \xlabel{eqn:mu-constraint-1}
i (E \partial _{\tau} \ln (F^{-}) - p \partial _{\sigma} \ln (F^{-})) = - \mu ^2
\end{equation}
can be used to find the explicit dependence of $\mu ^2$ on the quantum geometry parameters $k \Delta$ as
\begin{eqnarray}
 \xlabel{eqn:mu-constraint-final}
\mu ^2 &=& \frac{i}{\dfrac{2 \e ^{2 \phi}}{k \Delta} - 1} \bigm( p \del _{\sigma} \ln \left( \e^{2 \phi} / \Delta \right) - \nonumber\\\nf&&
- E \del _{\tau} \ln \left( \e^{2 \phi} / \Delta \right) \bigm) .
\end{eqnarray}

@@

From our analysis of the inverse-area corrected Polyakov action, we got $D$ finite-space one-dimensional Klein--Gordon Eqs.~\neqref{eqn:X-Klein-Gordon-eqn}, with constraints given by Eq. \neqref{eqn:inverse-area-em-tensor}. The constraints are nothing new, they are the same as the ones of regular String Theory. What is new in our analysis is the $\mu ^2$ term, which we take as being constant for a first analysis, making it so the solution is given by Fourier transform
\begin{eqnarray}
 \xlabel{eqn:KG-Polyakov-solution-initial}
X^{\mu} (\tau, \sigma) &=& \sqrt{\frac{\alpha '}{2}} \sum _{p \in \mathbb{Z}} \frac{1}{2 E_{p}} \biggm( \alpha ^{\mu} _{p} \e ^{i (E_{p} \tau - p \sigma)} + \nonumber\\\nf&&
+ \beta ^{\mu} _{p} \e ^{- i (E_{p} \tau - p \sigma)} \biggm),
\end{eqnarray}
with $E_{p} = \sqrt{p^2 + \mu ^2}$. From here on, following an analogous procedure to the one found in~\cite{Tong2009Lectures}, reality of $X^{\mu}$ implies $(X^{\mu})^{*} = X^{\mu}$, from which we get
\begin{equation}
 \xlabel{eqn:reality-consequence}
\beta ^{\mu} _{n} = (\alpha ^{\mu} _{n})^{*} .
\end{equation}
When looking at the constraints, we see that we cannot decouple the exponentials in $\tau$ from any of the sums, thus we get two-indices \textquotedblleft Virasoro modes"
\begin{subequations}
\begin{align}
L_{n, p} \coloneq  \alpha ^{\mu} _{n} \alpha ^{\nu} _{p} \eta _{\mu \nu}                                                         & = 0, \ \forall \ n, p \in \mathbb{Z}, \xlabel{eqn:"virasoro"-modes-1} \\
\widetilde{L}_{n, p} \coloneq  \alpha ^{\mu} _{n} (\alpha ^{\nu} _{p})^{*} \eta _{\mu \nu}                                       & = 0, \ n \neq p, \xlabel{eqn:"virasoro"-modes-2}                       \\
\sum _{n} \left( \left( 1 + \frac{n}{E_{n}} \right) ^2 \alpha ^{\mu} _{n} (\alpha ^{\nu} _{n})^{*} \eta _{\mu \nu} \right) & = 0 \xlabel{eqn:"virasoro"-modes-sum} .
\end{align}
\end{subequations}
Constraint \neqref{eqn:"virasoro"-modes-2} implies that we only have $D$ independent expansion modes for each field $X^{\mu}$, which for consistency as we will see later means $\alpha ^{\mu} _{- p} = \alpha ^{\mu} _{p}, \ p \leq d = D - 1$ and $\alpha ^{\mu} _{n} = 0, \ \forall \ \svert n\svert  > d$, so we have a truncated solution. This is not surprising, since because space--time is discrete we expect wavelengths smaller than the granular structure to be ruled out.

@@

\frac{\alpha '}{8} M^2 &=& \Biggm( \frac{2 \mu ^2}{\alpha '} \lfleft\lvert   \frac{\partial \psi (p)}{\partial p} \rfright\rvert   ^2 - \nonumber\\\nf&&

@@

\frac{\alpha '}{16} p^2 &=& a - \left( 1 + \frac{n^2}{n^2 + \mu ^2} \right) \sqrt{n^2 + \mu ^2} = \nonumber\\\nf&&

>>>>

Now, one might object and say that having an action which is the sum of two Nambu--Goto actions seems strange. However, similar actions have been extensively studied under the heading of ``bimetric gravity'', with the
earliest work dating as far back as 1940 in two papers~\cite{Rosen1940General,Rosen1940aGeneral} by Einstein's future collaborator Nathan Rosen (the `R' in `EPR' and `ER'). In 2010, bimetric gravity gained great popularity
due to the seminal paper~\cite{de-Rham2011Resummation} which showed that by introducing a second {reference} metric into a model for massive gravity one can get rid of the Boulware--Deser
ghost~\cite{Boulware1972Can-Gravitation} which otherwise plagues theories with massive gravitons. The {reference} metric introduced in the work~\cite{de-Rham2011Resummation} was taken to be a flat metric. However
later work~\cite{Hassan2012Bimetric,Hassan2012Ghost-Free} showed that the second metric need not be flat and that an action of the following form:
\begin{equation}
\xlabel{eqn:hassan-bimetric}
S = M_g^2 \int \diff^4 x \sqrt{-g} R^{(g)} + M_f^2 \int \diff^4 x \sqrt{-f} R^{(f)}
+ 2 m^2 M^2_{eff} \int \diff^4 x \sqrt{-g}\sum_{n=0}^{4}\beta_n e_n (\sqrt{g^{-1} f}),
\end{equation}
where $g_{\mu\nu}$ and $f_{\mu\nu}$ are {arbitrary} metrics, $M_g^2, M_f^2$ are the Planck masses for the two sectors respectively. $R^{(g)}, R^{(f)}$ are the respective Ricci scalars for each sector. The third term is an interaction term which is responsible for making one of the gravitons massive while the other remains massless. $M^2_{eff}$ is an {effective} Planck mass given by:
\begin{equation}
\xlabel{eqn:hassan-effective-mpl}
M^2_{eff} = \left( \frac{1}{M^2_g} + \frac{1}{M^2_f} \right)^{-1}
\end{equation}

@@

Following the general procedure given in~\cite{Callan1985Strings}, we can couple the worldsheet to a bulk metric as follows:
\begin{equation}
\xlabel{eqn:polyakov-curved}
S_{P} = -\frac{T}{2} \int \diff^2 x \sqrt{-g} g^{ab} \partial_a X^\mu \partial_b X^\nu G_{\mu\nu},
\end{equation}
where $G_{\mu\nu}$ is now the bulk or target space metric. Using this form we can now write down the worldsheet Polyakov bimetric action for two bulk metrics:
\begin{equation}
\xlabel{eqn:polyakov-bimetric}
S_{PB} = -\frac{T}{2} \int \diff^2 x\sqrt{-g} g^{ab} \partial_a X^\mu \partial_b X^\nu G_{\mu\nu}
- \frac{T'}{2} \int \diff^2 x \sqrt{-h} h^{ab} \partial_a X^\mu \partial_b X^\nu H_{\mu\nu}
+ S_{int} [g, h, X].
\end{equation}

@@

T^{(G)} _{c d} \coloneq  G_{\mu \nu} \biggm( \partial _{c} X^{\mu} \partial _{d} X^{\nu}

@@

T^{(H)} _{c d} \coloneq  H_{\mu \nu} \biggm( \partial _{c} X^{\mu} \partial _{d} X^{\mu}

@@

\left( \delta _{a} ^{c'} \delta _{b} ^{d'} H_{\mu \nu} - \frac{1}{2 g} \Delta _{a c} \varepsilon ^{c c'} \Delta _{b d} \varepsilon ^{d d'} G_{\mu \nu} \right)

@@

S_{I A P} = - \frac{T}{2} \int \diff ^2 x \left( \sqrt{- g} - \frac{k \Delta}{2 \sqrt{- g}} \right) \times g^{a b} \partial _{a} X^{\mu} \partial _{b} X^{\nu} G_{\mu \nu} .

@@

The equations of motion for the world-sheet metric are completely unchanged by this correction,
\begin{equation}
 \xlabel{eqn:vary-wrt-g}
\frac{\delta S_{I A P}}{\delta g^{c d}} = 0
\end{equation}
which leads to the stress--energy tensor for the worldsheet:
\begin{equation}
 \xlabel{eqn:inverse-area-em-tensor}
T_{c d} \coloneq  \partial _{c} X^{\mu} \partial _{d} X^{\nu} G_{\mu \nu} - \frac{1}{2} g_{c d} g^{a b} \partial _{a} X^{\mu} \partial _{b} X^{\nu} G_{\mu \nu} = 0,
\end{equation}
from which we can extract the metric $g_{c d}$ as
\begin{equation}
 \xlabel{eqn:ws-metric}
g_{c d} = 2 f \partial _{c} X^{\mu} \partial _{d} X^{\nu} G_{\mu \nu},
\end{equation}
where the function $f$ is given by
\begin{equation}
 \xlabel{eqn:inverse-area-f}
\frac{1}{f} = g^{a b} \partial _{a} X^{\mu} \partial _{b} X^{\nu} G_{\mu \nu}
\end{equation}
just like the regular ST literature, thus the constraints are unchanged by our correction.

As for variation \wrt \ the embbeding fields $X^{\lambda}$, we have
\begin{equation}
 \xlabel{eqn:vary-wrt-X}
\frac{\delta S_{I A P}}{\delta X^{\lambda}} = 0
\end{equation}
\begin{equation}
 \xlabel{eqn:X-eom-inverse-area}
F^{-} \sqrt{- g} g^{a b} \partial _{a} \partial _{b} X^{\nu} G_{\lambda \nu} + \partial _{a} \left( F^{-} \sqrt{- g} g^{a b} \right) \partial _{b} X^{\nu} G_{\lambda \nu} = \frac{1}{2} F^{-} \sqrt{- g} g^{a b} \partial _{a} X^{\mu} \partial _{b} X^{\nu} \partial _{\lambda} G_{\mu \nu},
\end{equation}
where
\begin{equation}
 \xlabel{eqn:F-minus-def}
F^{-} \equiv 1 - \frac{k \Delta}{2 (- g)} .
\end{equation}
Since all 2-dimensional metrics are conformally flat~\cite{Schottenloher2008A-Mathematical}, we use conformal gauge $g_{a b} = \e ^{\phi (x)} \eta _{a b}$ and assume flat background $G_{\mu \nu} = \eta _{\mu \nu}$, to simplify Eq. \neqref{eqn:X-eom-inverse-area} into
\begin{equation}
 \xlabel{eqn:X-eom-simplified}
\eta ^{a b} \partial _{a} \partial _{b} X^{\mu} + \frac{1}{F^{-}} \eta ^{a b} \partial _{a} F^{-} \partial _{b} X^{\mu} = 0 .
\end{equation}
By expanding the definition of $F^{-}$ we get
\begin{equation}
 \xlabel{eqn:coupling-X-phi}
\eta ^{a b} \partial _{a} \partial _{b} X^{\mu} + \eta ^{a b} \frac{\left( 2 \del _{a} \phi - \del _{a} \ln (\Delta) \right)}{\dfrac{2 \e ^{2 \phi}}{k \Delta} - 1} \del _{b} X^{\mu} = 0,
\end{equation}
revealing a wave equation sourced by a coupling between the WS conformal factor, quantum of area field $\Delta$ and the embedding fields much akin to the dilaton field~\cite{Balthazar-t-backgrounds}. We will come back to
this in \xref{sec:emergent-dimensions}.

@@

If one were to calculate the equations of motion for the quantum of area field $\Delta _{a b}$ in the actions \neqref{eqn:modified-ng-action,eqn:inverse-metric-Polyakov} explored before, one would end up concluding that
either $\Delta _{a b} = 0$ or its determinant $\Delta = 0$ vanish. This happens because, as we explored in  \xref{sec:ws-kalb-ramond}, $\Delta _{a b}$ is actually related to the pullback of the Kalb--Ramond field $B_{\mu \nu}$, but
those actions were actions for the free string, not coupled to said field. The more complete picture would be thus to consider the (area-corrected) string now coupled to the Kalb--Ramond field~\cite{Tong2009Lectures}
\begin{equation}
 \xlabel{eqn:area-corrected-K-R-action}
S = - \frac{1}{4 \pi \alpha '} \int \diff ^2 x \left( \sqrt{- g} - \frac{1}{2} \frac{k \Delta}{\sqrt{- g}} \right)
\times \Bigl( g^{a b} \del _{a} X^{\mu} \del _{b} X^{\nu} G_{\mu \nu} - \varepsilon ^{a b} \del _{a} X^{\mu} \del _{b} X^{\nu} B_{\mu \nu} \Bigr),
\end{equation}
where  we can rewrite $\varepsilon ^{a b}$ in terms of $\Delta ^{a b}$ as
\begin{equation}
 \xlabel{eqn:area-corrected-K-R-action-v2}
S = - \frac{1}{4 \pi \alpha '} \int \diff ^2 x \left( \sqrt{- g} - \frac{1}{2} \frac{k \Delta}{\sqrt{- g}} \right) \times \Bigm( g^{a b} \del _{a} X^{\mu} \del _{b} X^{\nu} G_{\mu \nu}
- \sqrt{\Delta} \Delta ^{a b} \del _{a} X^{\mu} \del _{b} X^{\nu} B_{\mu \nu} \Bigm) .
\end{equation}
By varying this action \wrt $\Delta ^{c d}$ we get
\begin{equation}
 \xlabel{eqn:Delta-pullback}
\Delta _{c d} = \widetilde{f} \del _{c} X^{\mu} \del _{d} X^{\nu} B_{\mu \nu}
\end{equation}
with $\widetilde{f}$ given by
\begin{equation}
 \xlabel{eqn:1/f-tilde}
\frac{1}{\widetilde{f}} = \frac{1}{g + \dfrac{k \Delta}{2}} \Biggm( \frac{k \sqrt{\Delta}}{2} g^{a b} \del _{a} X^{\mu} \del _{b} X^{\nu} G_{\mu \nu} - \left( g + \frac{3 k \Delta}{4} \right) \Delta ^{a b} \del _{a} X^{\mu} \del _{b} X^{\nu} B_{\mu \nu} \Biggm),
\end{equation}
where if we take $g_{a b} = \del _{a} X^{\mu} \del _{b} X^{\nu} G_{\mu \nu}$ and $\del _{a} X^{\mu} \del _{b} X^{\nu} B_{\mu \nu} = \Delta _{a b} / \widetilde{f}$ this simplifies to
\begin{equation}
 \xlabel{eqn:f-tilde}
\widetilde{f} = - \frac{g + k \Delta}{k \sqrt{\Delta}},
\end{equation}
from which it is easy to see that the pullback of the Kalb--Ramond field $b_{a b} \coloneq  \del _{a} X^{\mu} \del _{b} X^{\nu} B_{\mu \nu}$ is given by
\begin{equation}
 \xlabel{eqn:WS-b-field}
b_{a b} = - \frac{1}{\dfrac{g}{k \Delta} + 1} \varepsilon _{a b},
\end{equation}
or equivalently that the relation between $\Delta _{a b}$ and $b_{a b}$ is
\begin{equation}
 \xlabel{eqn:Delta-b-relation}
\Delta _{a b} = \sqrt{\Delta} \varepsilon _{a b} = - \sqrt{\Delta} \left( \frac{g}{k \Delta} + 1 \right) b_{a b} .
\end{equation}
We thus see that the pullback of the Kalb--Ramond field is actually a tensor {density} of weight $- 1$, since the coefficient in Eq. \neqref{eqn:WS-b-field} is a true scalar and the Levi-Civita symbol is itself a density.

@@

\eqref{eqn:X-eom-simplified} seems a bit odd, but we can polish it by choosing a plane-wave ansatz for the embedding fields $X^{\mu} = X^{\mu} _{0} \e ^{-i (E \tau - p \sigma)}$ and using it to fix a form for the conformal factor $\e ^{\phi (x)}$ appearing in $F^{-}$. By using the ansatz in Eq. \neqref{eqn:X-eom-simplified}, it becomes
\begin{equation}
(E^{2} - p^{2}) X^{\mu} + i (E \partial _{\tau} \ln (F^{-}) - p \partial _{\sigma} \ln (F^{-})) X^{\mu} = 0,
\end{equation}
from which we can use the freedom in the conformal factor to fix the second term as $- \mu ^2 X^{\mu}$, with $- \mu ^2 = p^2 - E^2$ on-shell and this, in turn, implies that the derivatives of $\ln (F^{-})$ are given by
\begin{equation}
 \xlabel{eqn:derivatives-F-minus}
\partial _{\tau} \ln (F^{-}) = i E, \ \partial _{\sigma} \ln (F^{-}) = i p,
\end{equation}
thus we have
\begin{equation}
 \xlabel{eqn:ln-F}
\ln (F^{-}) = i (E \tau + p \sigma) + a, \ a \in \mathbb{C}
\end{equation}
\xpar\cvskip[-9pt]
\begin{equation}
 \xlabel{eqn:F-minus-exp}
F^{-} = A \e ^{i (E \tau + p \sigma)}, \ A \in \C
\end{equation}
\xpar\cvskip[-9pt]
\begin{equation}
 \xlabel{eqn:phi}
\e ^{\phi (x)} = \sqrt{\frac{k \Delta}{2 \left( 1 - A \e ^{i (E \tau + p \sigma)} \right)}} .
\end{equation}
It may seem problematic to have a complex conformal factor, but the complex structure comes from our ansatz for the embedding fields, and when we choose either the real or imaginary part of the latter it should also pick the respective component of $\e ^{\phi}$. With this choice, we thus turned Eq. \neqref{eqn:X-eom-simplified} into a Klein--Gordon equation
\begin{equation}
 \xlabel{eqn:X-Klein-Gordon-eqn}
\left( \partial _{\sigma} ^2 - \partial _{\tau} ^2 \right) X^{\mu} - \mu ^2 X^{\mu} = 0 .
\end{equation}
The imposition that
\begin{equation}
 \xlabel{eqn:mu-constraint-1}
i (E \partial _{\tau} \ln (F^{-}) - p \partial _{\sigma} \ln (F^{-})) = - \mu ^2
\end{equation}
can be used to find the explicit dependence of $\mu ^2$ on the quantum geometry parameters $k \Delta$ as
\begin{equation}
 \xlabel{eqn:mu-constraint-final}
\mu ^2 = \frac{i}{\dfrac{2 \e ^{2 \phi}}{k \Delta} - 1} \bigm( p \del _{\sigma} \ln \left( \e^{2 \phi} / \Delta \right)
- E \del _{\tau} \ln \left( \e^{2 \phi} / \Delta \right) \bigm) .
\end{equation}

@@

From our analysis of the inverse-area corrected Polyakov action, we got $D$ finite-space one-dimensional Klein--Gordon Eqs.~\neqref{eqn:X-Klein-Gordon-eqn}, with constraints given by Eq. \neqref{eqn:inverse-area-em-tensor}. The constraints are nothing new, they are the same as the ones of regular String Theory. What is new in our analysis is the $\mu ^2$ term, which we take as being constant for a first analysis, making it so the solution is given by Fourier transform
\begin{equation}
 \xlabel{eqn:KG-Polyakov-solution-initial}
X^{\mu} (\tau, \sigma) = \sqrt{\frac{\alpha '}{2}} \sum _{p \in \mathbb{Z}} \frac{1}{2 E_{p}} \biggm( \alpha ^{\mu} _{p} \e ^{i (E_{p} \tau - p \sigma)}
+ \beta ^{\mu} _{p} \e ^{- i (E_{p} \tau - p \sigma)} \biggm),
\end{equation}
with $E_{p} = \sqrt{p^2 + \mu ^2}$. From here on, following an analogous procedure to the one found in~\cite{Tong2009Lectures}, reality of $X^{\mu}$ implies $(X^{\mu})^{*} = X^{\mu}$, from which we get
\begin{equation}
 \xlabel{eqn:reality-consequence}
\beta ^{\mu} _{n} = (\alpha ^{\mu} _{n})^{*} .
\end{equation}
When looking at the constraints, we see that we cannot decouple the exponentials in $\tau$ from any of the sums, thus we get two-indices \textquotedblleft Virasoro modes"
\begin{subequations}
\begin{align}
L_{n, p} \coloneq  \alpha ^{\mu} _{n} \alpha ^{\nu} _{p} \eta _{\mu \nu}                                                         & = 0, \ \forall \ n, p \in \mathbb{Z}, \xlabel{eqn:"virasoro"-modes-1} \\
\widetilde{L}_{n, p} \coloneq  \alpha ^{\mu} _{n} (\alpha ^{\nu} _{p})^{*} \eta _{\mu \nu}                                       & = 0, \ n \neq p, \xlabel{eqn:"virasoro"-modes-2}                       \\
\sum _{n} \left( \left( 1 + \frac{n}{E_{n}} \right) ^2 \alpha ^{\mu} _{n} (\alpha ^{\nu} _{n})^{*} \eta _{\mu \nu} \right) & = 0 \xlabel{eqn:"virasoro"-modes-sum} .
\end{align}
\end{subequations}
Constraint \neqref{eqn:"virasoro"-modes-2} implies that we only have $D$ independent expansion modes for each field $X^{\mu}$, which for consistency as we will see later means $\alpha ^{\mu} _{- p} = \alpha ^{\mu} _{p}, \ p \leq d = D - 1$ and $\alpha ^{\mu} _{n} = 0, \ \forall \ \svert n\svert  > d$, so we have a truncated solution. This is not surprising, since because space--time is discrete we expect wavelengths smaller than the granular structure to be ruled out.

@@

\frac{\alpha '}{8} M^2 = \Biggm( \frac{2 \mu ^2}{\alpha '} \lfleft\lvert   \frac{\partial \psi (p)}{\partial p} \rfright\rvert^2 

@@

\frac{\alpha '}{16} p^2 a - \left( 1 + \frac{n^2}{n^2 + \mu ^2} \right) \sqrt{n^2 + \mu ^2} 
